Effects of the body force on the evacuation dynamics

### 2020-02-04 paper.tex
agregue una referencia de data empirica del perfil de velocidad
agregue la cita de plimpton

The value of $k_n$ affects the velocity all along the corridor. Fig.~\ref{vx_profile} shows the velocity profile ($v_x$ vs. the longitudinal coordinate $y$) for different $k_n$ values. For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe). This behavior was observed in empirical measurements reported in Ref.~\cite{}. As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\

If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be easily deformed. In this context, to deform means to have parts of the crowd that move faster than other parts of the crowd. \\

@@

To conclude section \ref{corridor}, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks. The walls in the corridors play a critical role that prevents pedestrians from detaching from each other. This effect has consequences such as increasing the connectivity of the contact network and flattening the velocity profile (thus reducing the strain rate). If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high. This leads to a "solidification" of the crowd that makes all the pedestrians walk at almost the same velocity. The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd. \\

>>>>

The value of $k_n$ affects the velocity all along the corridor. Fig.~\ref{vx_profile} shows the velocity profile ($v_x$ vs. the longitudinal coordinate $y$) for different $k_n$ values. For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe). This behavior was observed in empirical measurements reported in Ref.~\cite{zhang2013empirical}. As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6). In this scenario, the value of mean $v_x$ is much lower than on the case of soft pedestrians ($k_n=$0).\\

If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be easily ``deformed''. In this context, to deform means to have certain parts of the crowd that manage to move faster than other parts of the crowd. \\

@@

To conclude section \ref{corridor}, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks. The walls in the corridors play a critical role that prevents pedestrians from detaching from each other. This effect has consequences such as increasing the connectivity of the contact network and flattening the velocity profile (thus reducing the strain rate). If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high. This leads to a ``solidification'' of the crowd that makes all the pedestrians walk at almost the same velocity. The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd. \\
